Vagueness, Noise, and Signaling

### 2015-04-08 paper/version_03/paper.tex
Moved Section 4 to appendix.

The next section introduces the background against which the work
presented here can be appreciated. Section~\ref{sec:repl-diff-dynam}
introduces the replicator diffusion dynamic and Section~\ref{sec:diffusion-as-special}
elaborates on its relation with the replicator mutator
dynamic. Section~\ref{sec:exploring-rdd} explores the replicator
diffusion dynamic. Section~\ref{sec:discussion} reflects and compares
our approach to others.

@@

The formulation of the \rdd given and explored here is in terms of
behavioral strategies, not in terms of mixed strategies. Dynamics on
behavioral strategies assume that agents can adapt
their behavior locally, so to speak, i.e., independently at each
choice point. This greatly reduces the complexity of the dynamic and
simplifies numerical simulations. But it also points towards an
interpretation of the process as cultural evolution, rather than
biological evolution. Signaling strategies are not inherited as a
whole, but adapted piece-meal, e.g., by conditional imitation of
``local'' behavior at a given choice point (more below). Still, the
approach we suggest here is compatible with a formulation in terms of
mixed strategies and an interpretation as biological evolution as
well. In Section~\ref{sec:diffusion-as-special}, we
translate our initial formulation of the \rdd
into one using mixed strategies. Doing so identifies the \rdd as a
special case of the \rmd. For now, let us first focus on the
formulation of the dynamic in terms of behavioral strategies alone.

@@

The following section works out the relation between the \rdd and the \rmd.
Although this section is conceptually important, it is also rather
technical and not strictly necessary to appreciate the main point of
the paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Diffusion as mutation}
\label{sec:diffusion-as-special}

Based on Equations~(\ref{eq:construction-rec}) and
(\ref{eq:construction-sen}), we can formulate the desired
correspondence result, a proof for which is given in Appendix~\ref{sec:proofs}.

@@

The previous sections showed that the \rdd can be conceptualized as a
two-step procedure: we first calculate where the replicator dynamic
would take us, then apply diffusion. To understand the \rdd better, we
isolate the novel diffusion part in
Section~\ref{sec:iterated-diffusion}, before exploring how diffusion
and fitness-based selection interact in Section~\ref{sec:simulations}.

@@

The \rdd adds expected confusion of similar states to the \rd in
behavioral strategies. The result is an abstract evolutionary dynamic
that describes the most likely path of development of aggregate
population behavior in which any process of behavioral adaptation at
the agent level that is consistent with the \rd in behavioral
strategies is perturbed by systematic noise in the realization of the
agents' strategies. Given the use of behavioral strategies, an
interpretation as a process of cultural evolution is most salient,
according to which agents adapt their choice dispositions locally at
each choice point. But the \rdd is also extensible to biological
evolution on mixed strategies, in which case it is a special case of
the \rmd with mutation matrices derived from confusion matrices, as
shown in Section~\ref{sec:diffusion-as-special}.

@@

\section{Proof of Theorem}
\label{sec:proofs}

>>>>

The next section introduces the background against which the work
presented here can be appreciated. Section~\ref{sec:repl-diff-dynam}
introduces the replicator diffusion dynamic. Section~\ref{sec:exploring-rdd} explores the replicator
diffusion dynamic. Section~\ref{sec:discussion} reflects and compares
our approach to others.
In Appendix~\ref{sec:diffusion-as-special} we give a formal elaboration on the relation between the replicator diffusion dynamic and the replicator mutator dynamic.
This finding is not necessary to understand the main points of this paper regarding vagueness, hence its inclusion in an appendix.
We decided to nevertheless include it since it is related, conceptually interesting, and potentially valuable for future work related to the model introduced in this paper.

@@

The formulation of the \rdd given and explored here is in terms of
behavioral strategies, not in terms of mixed strategies. Dynamics on
behavioral strategies assume that agents can adapt
their behavior locally, so to speak, i.e., independently at each
choice point. This greatly reduces the complexity of the dynamic and
simplifies numerical simulations. But it also points towards an
interpretation of the process as cultural evolution, rather than
biological evolution. Signaling strategies are not inherited as a
whole, but adapted piece-meal, e.g., by conditional imitation of
``local'' behavior at a given choice point (more below). Still, the
approach we suggest here is compatible with a formulation in terms of
mixed strategies and an interpretation as biological evolution as
well. In Appendix~\ref{sec:diffusion-as-special}, we
translate our initial formulation of the \rdd
into one using mixed strategies. Doing so identifies the \rdd as a
special case of the \rmd. For now, let us first focus on the
formulation of the dynamic in terms of behavioral strategies alone.

@@

%The following section works out the relation between the \rdd and the \rmd.
%Although this section is conceptually important, it is also rather
%technical and not strictly necessary to appreciate the main point of
%the paper.

@@

The previous section argued that the \rdd can be conceptualized as a
two-step procedure: we first calculate where the replicator dynamic
would take us, then apply diffusion. To understand the \rdd better, we
isolate the novel diffusion part in
Section~\ref{sec:iterated-diffusion}, before exploring how diffusion
and fitness-based selection interact in Section~\ref{sec:simulations}.

@@

The \rdd adds expected confusion of similar states to the \rd in
behavioral strategies. The result is an abstract evolutionary dynamic
that describes the most likely path of development of aggregate
population behavior in which any process of behavioral adaptation at
the agent level that is consistent with the \rd in behavioral
strategies is perturbed by systematic noise in the realization of the
agents' strategies. Given the use of behavioral strategies, an
interpretation as a process of cultural evolution is most salient,
according to which agents adapt their choice dispositions locally at
each choice point. But the \rdd is also extensible to biological
evolution on mixed strategies, in which case it is a special case of
the \rmd with mutation matrices derived from confusion matrices, as
shown in Appendix~\ref{sec:diffusion-as-special}.

@@

\section{Diffusion as mutation}
\label{sec:diffusion-as-special}

Based on Equations~(\ref{eq:construction-rec}) and
(\ref{eq:construction-sen}), we can formulate the desired
correspondence result:

We can prove this theorem as follows.
%\section{Proof of Theorem}
%\label{sec:proofs}
